s.function

### 2022-05-26 src/hex_heatmaps.Rmd
new images

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, msoa11cd, dointr, doterm) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd

path.lookup <- "/hdd/internet_archive/archive/ONSPD_FEB_2017_UK.csv"
lookup <- read_csv(path.lookup) %>% 
  select(pcds, oseast1m, osnrth1m) %>% 
  dplyr::rename(pc = pcds)

@@

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

>>>>

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, msoa11cd, dointr, doterm) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd

path.lookup <- "/hdd/internet_archive/archive/ONSPD_FEB_2017_UK.csv"
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, oseast1m, osnrth1m) %>% 
  dplyr::rename(pc = pcds)

@@

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```
## hex heatmaps log transformed

path.out <- paste0(path, "/outputs/hex_log", n)

    #stat_binhex(bins=150) +
    stat_binhex(aes(fill=log(..count..)), bins=150) +
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

### 2022-05-26 src/s_la.Rmd
new images

library(tidyverse)
library(broom)
library(rprojroot)

@@

@@

```{r}
df.test <- df %>% filter(ladcd == "S12000033")

@@

@@

ggplot(df.country, aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  ylab("N. of websites") +
  ggtitle("Country")
  #scale_x_date(breaks = df.test$year) 
```

@@

@@

@@

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
library(rgdal)
library(sf)
library(modelr)

@@

## TODO

- speed, other metrics? 
- understand rsquare
- model LAs
- add SE for the line plots [link](https://stackoverflow.com/questions/26020142/adding-shade-to-r-lineplot-denotes-standard-error)

@@

```{r}
df.test <- df %>% filter(ladcd == "E06000002")

@@

rsquare(fit, df.country)

@@

df.country %>% 
  ggplot(aes(x = year, y = n) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.country$year), breaks = df.country$year) +
  geom_vline(xintercept = 2003) +
  ylab("N. of websites") +
  ggtitle("Country")
  #scale_x_date(breaks = df.test$year) 
```

@@

## Loop for S function estimation for Local Authorities keeping the model objects

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    select(year, ladcd, n) 
    #lm(n~year, data = .)
    #tryCatch(tidy(nls(n ~ SSlogis(year, Asym, xmid, scal), data = .)), , error=function(e) NULL)
  tryCatch(model <- (nls(n ~ SSlogis(year, Asym, xmid, scal), data = data)), error=function(e) NULL)
  model.name <- paste0("model.", i)
  assign(model.name, model)
  tryCatch(b.la <- tidy(model), error=function(e) NULL)

  tryCatch(b.la$r2 <- rsquare(model, data), error=function(e) NULL)

  tryCatch(a.la <-rbind(a.la,b.la), error=function(e) NULL)
}

a.la <- a.la %>% filter(term=="xmid") %>% 
  bind_cols(as.tibble(all.la)) %>% 
  #mutate(estimate = round(estimate, 0)) %>% 
  #summarise(r = range(r2))
  filter(p.value < 0.01 & 
         r2 > 0.9) %>%    # 376 / 376, all sig, 330 r2 > 0.9
  select(ladcd, estimate, r2, std.error) %>%
  mutate(fast = ifelse(estimate < 2003, "fast", "slow"))

# predictions 
pred <- tibble()
help <- tibble(year = 1996:2012)
for (i in all.la){
  model.name <- (paste0("model.", i))
  #assign(col.name, paste0("pred.", i))
  pred_ <- df %>% filter(ladcd == i) %>% 
    mutate(prednls = eval(call("predict", as.name(model.name))))  # "pred.{i}" :=
  help_ <- help %>% left_join(pred_)

  pred <- pred %>% bind_rows(help_) 
}

# plots
path.out <- paste0(path, "/outputs/lad_")

for (i in all.la){
p <- ggplot(pred %>% left_join(a.la) %>% 
              filter(ladcd == i), aes(x = year, y = n, color = fast) ) +
  geom_point() +
  geom_line(aes(y = prednls), size = 1) +
  scale_x_continuous("year", labels = as.character(df.test$year), breaks = df.test$year) +
  geom_vline(xintercept = pred %>% left_join(a.la) %>% filter(ladcd == i) %>% select(estimate) %>% first()) +
  ylab("N. of websites") + 
  labs(title = paste0(la@data %>% filter(LAD21CD== i) %>% select(LAD21NM) %>% first(), ", ", i)) +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"))

ggsave(p, filename = paste(path.out, i, ".png", sep = ""))

}
```

## Xmid frequency graph

```{r}
ggplot(a.la, aes(as.factor(round(estimate, 0)))) +
  geom_bar(fill = "#0073C2FF")
```

@@

## Survival

- pop.density
- income
- firms
- employment
- N/S
- London

Time series formula will look like this:

`coxph(Surv(tstart, tstop, infect) ~ treat + inherit + steroids, data =newcgd, cluster = id)`

This is what @perkins2005international should be using.
See p. 7 [here](https://cran.r-project.org/web/packages/survival/vignettes/timedep.pdf).

```{r}
library(survival)

test.surv.data <- a.la %>% mutate(status = 1) %>% 
  left_join(data.la, by = c("ladcd" = "LAD21CD")) %>% 
  left_join(df %>% filter(year == 2012), by = "ladcd")

cf <- coxph(Surv((estimate-1996), status) ~ log(distLondon) + log(distMet) + log(pop16_64) + log(pop.dens) + log(econ.act) + log(earnings) + log(total.busi) + south + log(n), data=test.surv.data, weights = 1/(std.error)^2)
summary(cf)

@@

## time series clusters

2 clusters is the preferred solution, but when I plot individual local authorities 
I cannot interpret the differences between the two clusters

```{r}
library(dtwclust)
library(tsbox)
library(imputeTS)

# turn to a wide format
ts.wide <- df %>% 
  filter(!is.na(ladcd)) %>% 
  rename(time = year) %>%
  dplyr::select(time, ladcd, n) %>% 
  #mutate(year = )
  ts_wide()

# impute with means of each TS
# TODO check sensitivity
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

# extract names
ts.wide.names <- names(ts.wide[,-1])
ts.wide <- ts.wide[,-1]

# standardise
ts.wide <- zscore(ts.wide)

# convert to list for tsclust
ts.wide <- split(ts.wide, rep(1:ncol(ts.wide), each = nrow(ts.wide)))

# 5 - 20 cluster sollutions
pc_k <- tsclust(ts.wide, k = c(2:10), seed = 94L,
                type="partitional",
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

# decide k, see RJ-2019-023 for max/min
#names(pc_k) <- paste0("k_", c("5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15"))
names(pc_k) <- paste0("k_", c("2", "3", "4", "5", "6", "7", "8", "9", "10"))
cvis <- sapply(pc_k, cvi, type = "internal")
cvis
# max Sil
# max SF
# max CH
# min DB
# min DBstar
# max D
# min COP

# loop for k decision
pref.cvi <- NULL

max.cvis <- c(1:3,6)
for (i in max.cvis){
  a <- which.max(cvis[i,])
  pref.cvi <- c(pref.cvi, a)
}

min.cvis <- c(4:5,7)
for (i in min.cvis){
  a <- which.min(cvis[i,])
  pref.cvi <- c(pref.cvi, a)
}

print(pref.cvi) # just count how many time each k_* appears, this is the preferred solution

pc_k <- tsclust(ts.wide, k = 7, seed = 94L,  # 7 or 2
                type="partitional", 
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))
plot(pc_k)

clusters <- data.frame(LAD=ts.wide.names,
                           cluster=pc_k@cluster)

## Mapping the clusters

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}

la.f <- la.f %>% left_join(clusters, by = c("id" = "LAD")) %>% 
  arrange(order)  # if i don't order merge.nuts.f loses order and the map has gaps

ggplot(la.f %>% filter(!is.na(r2)), aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster))) +
  #theme_nothing(legend = TRUE) +
  labs(title = "Clusters") +
  scale_fill_viridis_d()+
  theme_void()

# ggplot(la.f, aes(x = long, y = lat)) +
#   geom_polygon(aes( group = group, fill = as.factor(cluster.down))) +
#   theme_nothing(legend = TRUE) +
#   labs(title = "Download clusters") +
#   scale_fill_viridis_d()+
#   theme_void()
# 
# cluster.upL <- c(6, 9, 11, 12, 13)
# cluster.upS <- c(1, 2, 3, 7, 8, 10)
#  
# la.f_ <- la.f #plot the background
# 
# cluster.upL.plot <- la.f %>% 
#   filter(cluster.up %in% cluster.upL) %>% 
#   ggplot(aes(x = long, y = lat)) +
#   geom_polygon(data = la.f_, color='grey', fill='white', aes(x=long, y=lat, group=group, colour = 'grey30')) +
#   geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
#   labs(title = "Larger clusters, upload speeds") + 
#   scale_fill_viridis_d() +
#   guides(fill=guide_legend(title="Clusters")) +
#   theme_void()
# 
# cluster.upS.plot <- la.f %>% 
#   filter(cluster.up %in% cluster.upS) %>% 
#   ggplot(aes(x = long, y = lat)) +
#   geom_polygon(data = la.f_, color='grey', fill='white', aes(x=long, y=lat, group=group, colour = 'grey30')) +
#   geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
#   labs(title = "Smaller clusters, upload speeds") + 
#   scale_fill_viridis_d() +
#   guides(fill=guide_legend(title="Clusters")) +
#   theme_void()
# 
# plot_grid(cluster.upL.plot, cluster.upS.plot, nrow = 1,
#           align = "h", axis = "l", 
#           #labels = c(".co.uk / pop., 2000", ".co.uk / pop., 2010", "non .co.uk / pop., 2000", "non .co.uk / pop., 2010", ""), 
#           #label_size = 12,
#           greedy = T)
#           #rel_heights = c(1, 1, .3)) # this is the relative position of the 3 lines
# 
# #ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters.png")
# ggsave(out.path.map)#,
#        #width = 210, #A4
#        #height = 297, #A4
#        #units = "mm")
```
